Schema Evolution in Interactive Programming Systems

### 2024-08-28 paper.tex
fix pluralization typo

The challenge of maintaining multiple divergent schema in programming systems can
be well illustrated using \emph{multiplicity change}, which is a common kind of schema change.
In this case a field changes from storing
a single value to storing multiple values. For example, we might start by storing a single
address for each contact in an address book, before realizing that we need to store multiple
addresses for a single contact. Alternatively, we might assign each todo in a list to one person before
realizing we want the ability to assign a todo to multiple people.

>>>>

The challenge of maintaining multiple divergent schemas in programming systems can
be well illustrated using \emph{multiplicity change}, which is a common kind of schema change.
In this case a field changes from storing
a single value to storing multiple values. For example, we might start by storing a single
address for each contact in an address book, before realizing that we need to store multiple
addresses for a single contact. Alternatively, we might assign each todo in a list to one person before
realizing we want the ability to assign a todo to multiple people.
